---
title: "Assignment 2"
author: "Matthew Mayor"
date: "9/8/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For this assignment, I had to collect opinions of recent popular movies from people I know and record them in a SQL database and then load that database into R.

I started by creating and populating the database in MySQL.

These are the SQL commands I performed to do this:

CREATE DATABASE movies;

CREATE TABLE rottencucumbers (

id INT NOT NULL AUTO_INCREMENT,
	
firstname VARCHAR(100) NOT NULL,
    
captainmarvel INT,
    
avengersendgame INT,
    
midsommar INT,
    
toystory4 INT,
    
spidermanffh INT,
    
lionking INT,
    
PRIMARY KEY (id)
    
);

INSERT INTO rottencucumbers (firstname, captainmarvel, avengersendgame, midsommar, toystory4, spidermanffh, lionking)

VALUES ('Matt', 3, 5, 5, null, 2, null),
	   
('Emily', null, null, 5, null, null, null),
       
('Josephine', 3, 5, null, null, 3, null),
       
('Nicole', 5, 5, null, null, 4, null),
       
('Jessica', 4, 5, null, null, null, null);

As you might be able to see, the people I surveyed had not been to many movies recently.

In R, I used the DBI and RMySQL packages.  I started by loading each of them.

```{r}
library(DBI)
library(RMySQL)
```

I then proceeded to establish the connection.

```{r}
mysql <- dbDriver("MySQL")
con <- dbConnect(mysql, dbname = 'movies', user = 'data607', password = 'data607', host = 'localhost')
```

I then use the dbGetQuery() function to load my table into a dataframe.

```{r}
movies <- dbGetQuery(con, "SELECT * FROM rottencucumbers")
```

Last, I loaded the dataframe to check that everything worked.

```{r}
movies
```
