---
title: "Assignment3"
author: "Matthew Mayor"
date: "9/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The first problem for this assignment involved manipulating strings using stringr and regular expressions.

I started by loading the "stringr" package and the data for the problem.

```{r}
library(stringr)
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555 -6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name
```

My first task was to make sure all the names were in a first name last name format.  For this I used the str_replace_all function.

```{r}
name <- str_replace_all(name, "(.+,)(.+)", "\\2 \\1")
name
```

At this point, they were almost there, but needed a tiny bit of cleaning up.

```{r}
name <- str_trim(name)
name <- str_replace_all(name, ",", "")
name
```

Now that they were formatted correctly, I could address the next two tasks.

First, I had to get a logical vector indicating which names had titles.

```{r}
title <- str_detect(name, "^[[:alpha:]]{2,3}[.]")
title
```

And then I had to get a logical vector indicating which characters have a second name.

```{r}
mult_names <- str_detect(name, "^[[:alpha:]][.]")
mult_names
```

For the next problem, I had to analyze a few regular expressions.

1.

```{r}
exp1 <- "[0-9]+\\$"
str_detect("405$",exp1)
```

This matches one or more digits followed by a dollar sign.  I.e. 405$.

2.

```{r}
exp2 <- "\\b[a-z]{1,4}\\b"
str_detect("goat",exp2)
```

This matches a one-to-four letter all lowercase word. I.e. "goat"

3. 

```{r}
exp3 <- ".*?\\.txt$"
str_detect("hidden.txt",exp3)
```

This matches a string ending in .txt and whatever precedes it. I.e. "hidden.txt"

4.

```{r}
exp4 <- "\\d{2}/\\d{2}/\\d{4}"
str_detect("09/22/2004",exp4)
```

This matches a date format where the month and day are represented by two digits and the year by four.  I.e. "09/22/2004"

5.

```{r}
exp5 <- "<(.+?)>.+?</\\1>"
str_detect("<urgent> vote blue </urgent>",exp5)
```

This matches a string contained in \<\> followed by any string followed by \</\> with the original string appearing.  Example can be seen in the R code above.


Extra credit: For extra credit I decode the message.

```{r}
code <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5 fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
code <- str_replace_all(code, "[[:digit:][:lower:][:space:]]", "")
code
```

The code reads "Congratulations you are a supernerd!"
