---
title: "Assignment 5"
author: "Matthew Mayor"
date: "9/29/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

To start on this assignment, I loaded all the necessary libraries: plyr, dplyr, tidyr, and ggplot2.

```{r}
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)
```

I then loaded the CSV file from GitHub where I uploaded it.

```{r}
flights <- read.csv("https://raw.githubusercontent.com/MJJMayor/DATA607/master/airlines.csv")
flights
```

As you can see, it needs some tidying.  First was to get rid of the empty row.

```{r}
flights <- slice(flights, c(1,2,4,5))
flights
```

Next, I needed to fill in the blank values in the first column with the appropriate airline.

```{r}
flights$X <- c("ALASKA","ALASKA","AM WEST", "AM WEST")
flights
```

Next was to fix the problem of some of the columns being values.

```{r}
flights <- gather(flights, "Dest", "Freq", 3:7)
flights
```

Next, was to rename the first two columns that were previously given default names.

```{r}
flights <- rename(flights, Airline = X, Arrival = X.1)
flights
```

Now, according to tidy rules, I had to reorder the columns so that the fixed values came before the observed values.  In doing so I put the destination before the arrival status.

```{r}
flights <- select(flights, Airline, Dest, Arrival, Freq)
flights
```

The table is now in tidy condition.  Next is to do some analysis.

I start by using ddply to create a new column that stores the proportion of flights with a certain arrival status grouped by airline and destination.

```{r}
flights <- ddply(flights, .(Airline,Dest), transform, prop = Freq/sum(Freq))
flights
```

Next, I used arrange() to revert the table to the same sorting it had previously.

```{r}
flights <- arrange(flights, Dest)
flights
```

Last, I plotted the proportion of on time arrivals at each airport between each airline in a bar plot.

```{r}
ggplot(data=flights, aes(x=Dest, y=prop, fill=Airline)) + geom_bar(stat="identity", position=position_dodge())
```

From this plot you can see that at every airport, ALASKA had a higher proportion of on time arrivals.  The difference is the starkest at San Francisco and Seattle.
